### 2017-10-10 Gruba/03-fe.tex

\stitle{Step 4:} Similarly, another metric \textit{Twitter-LDA weight} $W_w$ is obtained, i.e., using Twitter-LDA  %\ref{IEEEexample:zhao2011comparing} 
\refe{}
to result the word weight distribution of blog $b$.
Unlike TF-IDF, Twitter-LDA first trains the overall blogs, allocating each blog with a \textit{tag}.
%
The structure of \textit{tag} is as follows:
\begin{equation}
\label{eq:tw-tag}
W_t = \{(w'_i, p'_i)\}
\end{equation}
where $w'_i$ refers to a word in \textit{tag} $W_t$, and $p'_i$ is the probability that $w'_i$ appears in blogs with the said \textit{tag}, with $\sum_{\substack{i}} p'_i = 1$ ($|W_t|\ =\ 30$ in this work by default).
%
Subsequently, $W_t$ are leveraged to conclude $W_w$, i.e., $W_w\ =\ W_t$ , which shares the format with that of $W_f$.
Go to \textbf{Step 6}.

\stitle{Step 5:} TF-IDF based similarity is calculated.
For example, the similarity (in the form of a value) of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined as:
\begin{equation}
\label{eq:sim-tf1}
sim(W_f, t) = \sum_{\substack{i}} p_i*sim(w_i, t)
\end{equation}
where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector \refe{}.
Go to \textbf{Step 7}.

@@

\stitle{Step 6:} Accordingly, Twitter-LDA based similarity is available.
Again, a single topic $t$ in lexicon is used for yardstick and the similarity of $W_w$ over $t$, written as $sim(W_w, t)$, is defined as:
\begin{equation}
\label{eq:sim-tw1}
sim(W_w, t) = \sum_{\substack{i}} p'_i*sim(w'_i, t)
\end{equation}
where $W_w = \{(w'_i, p'_i)\}$, $t = \{c_j\}$, and $sim(w'_i, t)$ is the averaged word similarity $sim(w'_i, c_j)$ returned by word2vector \refe{}.
Go to \textbf{Step 7}.

>>>>

\stitle{Step 4:} Similarly, another metric \textit{Twitter-LDA weight} $W_w$ is obtained, i.e., using Twitter-LDA  %\ref{IEEEexample:zhao2011comparing}
\cite{IEEEexample:zhao2011comparing}
to result the word weight distribution of blog $b$.
Unlike TF-IDF, Twitter-LDA first trains the overall blogs, allocating each blog with a \textit{tag}.
%
The structure of \textit{tag} is as follows:
\begin{equation}
\label{eq:tw-tag}
W_t = \{(w'_i, p'_i)\}
\end{equation}
where $w'_i$ refers to a word in \textit{tag} $W_t$, and $p'_i$ is the probability that $w'_i$ appears in blogs with the said \textit{tag}, with $\sum_{\substack{i}} p'_i = 1$ ($|W_t|\ =\ 30$ in this work by default).
%
Subsequently, $W_t$ are leveraged to conclude $W_w$, i.e., $W_w\ =\ W_t$ , which shares the format with that of $W_f$.
Go to \textbf{Step 6}.

\stitle{Step 5:} TF-IDF based similarity is calculated.
For example, the similarity (in the form of a value) of $W_f$ over a single topic $t$ in lexicon, written as $sim(W_f, t)$, is defined as:
\begin{equation}
\label{eq:sim-tf1}
sim(W_f, t) = \sum_{\substack{i}} p_i*sim(w_i, t)
\end{equation}
where $W_f = \{(w_i, p_i)\}$, $t = \{c_j\}$, and $sim(w_i, t)$ is the averaged word similarity $sim(w_i, c_j)$ returned by word2vector \cite{IEEEexample:mikolov2013distributed}.
Go to \textbf{Step 7}.

@@

\stitle{Step 6:} Accordingly, Twitter-LDA based similarity is available.
Again, a single topic $t$ in lexicon is used for yardstick and the similarity of $W_w$ over $t$, written as $sim(W_w, t)$, is defined as:
\begin{equation}
\label{eq:sim-tw1}
sim(W_w, t) = \sum_{\substack{i}} p'_i*sim(w'_i, t)
\end{equation}
where $W_w = \{(w'_i, p'_i)\}$, $t = \{c_j\}$, and $sim(w'_i, t)$ is the averaged word similarity $sim(w'_i, c_j)$ returned by word2vector.
Go to \textbf{Step 7}.
